---
title: 'STAC32 Assignment #1'
author: "Grisham Nathan 1001314927"
date: "September 14, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#a)
```{r}
library(tidyverse)
url="http://www.utsc.utoronto.ca/~butler/c32/global.csv"
input=read_csv(url)
input 
```
Reads data from the CSV file from the URL and stores in variable. 
Afterwards, it is then outputted in a data frame.
The data frame has 10 rows and 3 columns.


#b)
```{r}
ggplot(input,aes(x=size,y=cost))+geom_point()
```
Creates scatterplot using the data frame, using the size column as the x-axis and the cost as my y-axis.
The points are added according to corresponding size and cost of each observation.

#c)
There is a positive relationship between size and cost. As
size increases, cost also increases. 

The trend appears to go from bottom left to top right.   
A straight regression line would describe the trend 
appropriately, however their are some points that 
slightly deviate from the regression line.

#d)
ggplot(input,aes(x=size,y=cost,colour=warehouse))+geom_point()

I think size determines which warehouse an incoming shipment goes to. From the data given and the scatterplot I created, the largest shipment to warehouse A is 225000 parts and the smallest shipment to warehouse B is 290000 parts. It seems that whether a shipment has more or less than a certain number of parts (Definitely between 225000 and 290000 parts), is what determines which warehouse the shipment goes.

As a result, we can infer that products below this specified limit goes to warehouse A and products above this specified limit go to warehouse B. 






 