---
title: "Assignment 3"
author: "Grisham Nathan 1001314927"
date: "September 24, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#A)
```{r}
library(tidyverse)
myurl = "http://www.utsc.utoronto.ca/~butler/c32/hg.txt" 
mydata = read_delim(myurl, " ") 
mydata
```

I have the correct variables.Just as used as column names in the hg.txt, the variables are name and density. 13 hunter-gatherer societies in Australia were studied, as there are 13 rows.

#B)

Let h0 be h not which is the null hypothesis
Let hA be the alternative hypothesis
let u be mu which is the mean 

We have h0: u = 7.38 which means the mean density of the socities match the rest of the world
We have hA: u =/= 7.38 mean the mean population density is not the same

#C)
```{r}
t.test(mydata$density, mu=7.38)
```
I tested the hypotheses using one sample t-test. 
The P-value is 0.002257.
Since p-value is lower than 0.05, we will reject null hypothesis.


#D)
```{r}
mybins = ceiling(log(13,2))+1
ggplot(mydata,aes(x=density))+geom_histogram(bins=mybins)
qqnorm(mydata$density)
qqline(mydata$density)
```
It is noticable that the histogram is skewed as it decreases to the right.
We know that if the histogram of the data accuretly follows a normal distributions
our p-value is good and we cannot reject the H0. Therefore in this case
it is very far from being a proper normal distribution hence the p value will also be off
so we can reject H0.I do not have doubts of the validity of the test. 






