---
title: "Assignment 8"
author: "Grisham Nathan"
date: "November 15, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#11
#a)
```{r}
library(tidyverse)
url="http://stat405.had.co.nz/data/billboard.csv"
billboard=read_csv(url)
billboard
```

#b)
```{r}
billboard %>% gather(Week,Rank,x1st.week:x76th.week,na.rm=T)
```
I have fewer columns after converting the columns from before. I have alot more rows because each song must indicate each week and the corresponding rank of the week.

#c)
```{r}
billboard %>% gather(Week,Rank,x1st.week:x76th.week,na.rm=T) %>% select(Week,Rank) %>% head
```

#d)
```{r}
billboard %>% gather(Week,Rank,x1st.week:x76th.week,na.rm=T) %>% mutate(Week_numeric=parse_number(Week), Rank_numeric=as.numeric(Rank)) %>% select(Week_numeric, Rank_numeric)
```

#e)
```{r}
billboard %>% gather(Week,Rank,x1st.week:x76th.week,na.rm=T) %>% mutate(Week_numeric=parse_number(Week), Rank_numeric=as.numeric(Rank)) %>% mutate(current=parse_date(date.entered)+(Week_numeric-1)*7) %>% select(date.entered, Week_numeric, current)
```

#f)
```{r}
billboard %>% gather(Week,Rank,x1st.week:x76th.week,na.rm=T) %>% mutate(Week_numeric=parse_number(Week), Rank_numeric=as.numeric(Rank)) %>% mutate(current=parse_date(date.entered)+(Week_numeric-1)*7) %>% filter(Rank_numeric == 1) %>% select(artist.inverted, track,current) %>% arrange(current)
```

#g) 
```{r}
billboard %>% gather(Week,Rank,x1st.week:x76th.week,na.rm=T) %>% mutate(Week_numeric=parse_number(Week), Rank_numeric=as.numeric(Rank)) %>% mutate(current=parse_date(date.entered)+Week_numeric*7-1) %>% filter(Rank_numeric == 1) %>% group_by(artist.inverted,track) %>% count(track)%>% arrange(desc(n)) %>% head(1)
```

##12)
#a)
```{r}
url = "http://www.utsc.utoronto.ca/~butler/c32/pinetrees.txt"
pine=read_delim(url, " ")
pine
```

#b)
```{r}
ggplot(pine,aes(x=diameter, y=volume)) + geom_point()
```

#c)
There is positive relationship between diameter and volume. As diameter of tree increases, the volume of tree also increases.

#d)
```{r}
reg=lm(volume~diameter,pine)
summary(reg)
```
R-Squared is 0.9585, which means there is a very strong positive linear relationship between diameter and volume.

#e)
```{r}
ggplot(reg,aes(x=.fitted,y=.resid))+geom_point() +geom_smooth(se=F)
```
I do not trust the linearity of this regression. The residual plot does not show a straight line more or less at 0. As a result, we conclude that linear regression is not suitable for modeling the relationship between diameter and volume.

#f)
The volume of a tree of diameter of zero should be 0.No it is not what the regression predicts. According to my regression, when diameter is 0, volume is -191.749. Volume is suppose to be zero when diameter is 0.

#g)

cone_volume = (pi*((d/2)^2)*h)/3

where h = height and d = diameter

#h) 
```{r}
h=2
cone_volume = (pi*((pine$diameter/2)^2)*h)/3
reg_cone=lm(cone_volume~I((pine$diameter)^2))
summary(reg_cone)
```