---
title: 'Assignment #6'
author: "Grisham Nathan"
date: "October 23, 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(devtools)
install_github("nxskok/smmr")
library(smmr)
```

##4.
#a)
```{r}
library(tidyverse)
url="http://www.utsc.utoronto.ca/~butler/c32/forehead.txt"
forehead=read_delim(url," ")
forehead %>% slice(1:10)
```

#b)
```{r}
ggplot(forehead,aes(x=group,y=score))+geom_boxplot()
#ggplot(forehead,aes(sample=score))+stat_qq()+facet_wrap(~group)
```

#c)

Their is an outlier in each group and the boxplot for each group is not symmetric. As a result, this violates the assumption of the t-test that data must be normally distributed. As a result, we can conclude that our two-sample t-test is not valid.


#d)
```{r}
m=median(forehead$score)
m
tab=with(forehead,table(group,score>m))
tab
chisq.test(tab,correct=F)
```
Given the small p-value, I conclude that the data being above/below overall median depends on the group.Both groups have different medians.I recommend that the video be watched at 8:30 am.


#e)
```{r}
median_test(forehead,score,group)
```
I got the same answer as d)

##5.
#d)
```{r}
url="http://www.utsc.utoronto.ca/~butler/c32/movie-lengths.csv"
movie=read_csv(url)
movie.aov=aov(length~rating, data=movie)
summary(movie.aov)
TukeyHSD(movie.aov)
```